\documentclass[a4paper,10pt]{article}
%\documentclass[a4paper,10pt]{scrartcl}
\usepackage[margin=1in,footskip=0.25in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{outline}
\usepackage{multicol}
\usepackage{tabularx}
\title{}
\author{Will Dampier}
\date{}

\pdfinfo{%
  /Title    ()
  /Author   ()
  /Creator  ()
  /Producer ()
  /Subject  ()
  /Keywords ()
}

\renewcommand{\theenumi}{\Alph{enumi}}

\begin{document}
\begin{enumerate}
 \item NAME \newline
 William Dampier
 \item HOME AND PROFESSIONAL MAILING ADDRESS
 \begin{itemize}
  \item[] Home Address
  \begin{itemize}
   \item[] 226 W. Rittenhouse Sq, Apt 2213
   \item[] Philadelphia, PA, 19103
   \item[] Cell Phone Number: (267) 403-0049
  \end{itemize}
  \item[] Professional Address
  \begin{itemize}
   \item[] Drexel University College of Medicine
   \item[] Department of Microbiology and Immunology
   \item[] 18th Floor New College Building
   \item[] Rm. 18105
   \item[] 245 N. 15th Street
   \item[] Philadelphia, PA 19102
   \item[] (215) 762-7340
   \item[] Electronic Mail:  wnd22@drexel.edu
  \end{itemize}
 \end{itemize}
 \item EDUCATION \newline
 \begin{tabular}{p{0.15\textwidth}p{0.01\textwidth}p{0.65\textwidth}}
  2001-2006 & & Drexel University, Philadelphia, Pennsylvania \newline Major: Bioinformatics \newline Awarded Bachelor of Science degree \\
  2006-2010 & & Drexel University, Philadelphia, Pennsylvania \newline School of Biomedical Engineering and Health Sciences \newline Awarded Doctoral Degree \\
 \end{tabular}
 \item POSTGRADUATE TRAINING \newline
 \begin{tabular}{p{0.15\textwidth}p{0.01\textwidth}p{0.65\textwidth}}
  2001-2006 & & Postdoctoral Researcher \newline Department of Computational Biology \newline GlaxoSmithKline Collegeville, Pennsylvania \newline Under the direction of Dr. Jim Brown, Director \\
 \end{tabular}
 \item EMPLOYMENT HISTORY \newline
  \begin{tabular}{p{0.15\textwidth}p{0.01\textwidth}p{0.65\textwidth}}
  2002-2003 & & Research Assistant \newline Viropharma Inc. \newline Chester Springs, Pennsylvania \newline Research Interest: Small molecule inhibitors of Hep-C Virus\\
  \\
  2003-2004 & & Research Assistant \newline NovaFlora Inc. \newline Philadelphia, Pennsylvania \newline Research Interest: Genetic engineering of ornamental flowers\\
  \\
  2004 & & Research Assistant \newline GlaxoSmithKline \newline Upper Providence, Pennsylvania \newline Research Interest: Alzheimer’s research in \emph{C. elegans}\\
  \\
  2005-2006 & & Research Assistant \newline University of Pennsylvania \newline Department of Microbiology \newline Philadelphia, Pennsylvania \newline Research Interest: Entry methods of L. monocytogenes\\
  \\
  2008-2013 & & Assistant Director \newline Center for Integrated Bioinformatics \newline Drexel University, School of Biomedical Engineering \newline Philadelphia, Pennsylvania\\
  \\
  2011-2013 & & Research Assistant Professor \newline Drexel University \newline School of Biomedical Engineering \newline Philadelphia, Pennsylvania\\
  \\
  2013-present & & Research Assistant Professor \newline Department of Microbiology and Immunology \newline Drexel University College of Medicine \newline Philadelphia, Pennsylvania\\
 \end{tabular}
 \item CERTIFICATION AND LICENSURE \newline
 N/A
 \item MILITARY SERVICE \newline
 N/A
 \item HONORS AND AWARDS \newline
 \begin{tabular}{p{0.15\textwidth}p{0.01\textwidth}p{0.65\textwidth}}
  2009 & & 6th place in the Matlab Programming Contest. \newline More then 6000 entries world-wide\\
  \\
  2007 & & 2nd Place, Most Innovative Technology Poster \newline School of Biomedical Engineering and Health Systems, Drexel University \newline Philadelphia, Pennsylvania\\
  \end{tabular}
 \item MEMBERSHIPS IN PROFESSIONAL SOCIETIES \newline
  \begin{tabular}{p{0.15\textwidth}p{0.01\textwidth}p{0.65\textwidth}}
  2013-present & & The International Society of NeuroVirology\\
  \end{tabular}
 \item PROFESSIONAL COMMITTEES AND ADMINISTRATIVE SERVICE
 \begin{itemize}
  \item[] Institutional Service \newline
  \begin{tabular}{p{0.15\textwidth}p{0.01\textwidth}p{0.65\textwidth}}
  2010-present & & Senior Design Committee Member \newline Drexel University, School of Biomedical Engineering \newline Philadelphia, Pennsylvania \\
  \\
  2012-present & & Senior Design Committee Advisor \newline Drexel University, School of Biomedical Engineering \newline Philadelphia, Pennsylvania \\
  \end{tabular}
  \item[] Extramural Service \newline
  \begin{tabular}{p{0.15\textwidth}p{0.01\textwidth}p{0.65\textwidth}}
  2011-present & & Python Core Contributor \\
  2011-present & & Python Scipy Contributor \\
  2011-present & & Python Django Contributor \\
  2011-present & & Python Scikits-Learn Contributor \\
  \end{tabular}
  \item[] Journal Editorial and Review Responsibilities \newline
  \begin{tabular}{p{0.15\textwidth}p{0.01\textwidth}p{0.65\textwidth}}
  2010-present & & BMC Bioinformatics (Reviewer) \\
  2011-present & & BMC Medical Genomics (Reviewer) \\
  2012-present & & International Journal of Genomics (Reviewer) \\
  \end{tabular}
 \end{itemize}
 \item COMMUNITY SERVICE \newline
 NA
 \item EDUCATIONAL ACTIVITIES
 \begin{itemize}
  \item[] Teaching Experience \newline
   \begin{tabular}{p{0.15\textwidth}p{0.01\textwidth}p{0.65\textwidth}}
  2008-present & & Head Instructor \newline Drexel Judo Club (10 hours/week) \newline Drexel University \newline Philadelphia, Pennsylvania \\
  \\
  2010-2012 & & Head Instructor \newline UPenn Judo Club (4 hours/week) \newline University of Pennsylvania \newline Philadelphia, Pennsylvania \\
  \\
  2010-2011 & & Adjunct Professor, (BMES 505-507) \newline Math for Biomedical Scientist (3 credits each) \newline Drexel University School of Biomedical Engineering \newline Philadelphia, Pennsylvania \\
  \\
  2010-present & & Adjunct Professor, (BMES 375) \newline Computational Biology (4.5 credits) \newline Drexel University School of Biomedical Engineering \newline Philadelphia, Pennsylvania \\
  \end{tabular}
 \end{itemize}
 \item CLINICAL ACTIVITIES \newline
 N/A
 \item GRANT SUPPORT
 \item GRADUATE STUDENTS, POSTDOCTORAL FELLOWS, AND   POSTGRADUATE MEDICAL TRAINEES
 \begin{itemize}
  \item[] Co-Supervision of Graduate Student Research \newline
    \begin{tabular}{p{0.15\textwidth}p{0.01\textwidth}p{0.65\textwidth}}
  2012-present & & Gregory Antell, School of Biomedical Engineering \newline Graduate Program (Ph.D degree student) \newline Drexel University \newline Philadelphia, Pennsylvania
  \end{tabular}
 \end{itemize}

 \item BIBLIOGRAPHY
 \begin{itemize}
  \item[] Published full-length papers
  \begin{enumerate}[label=\arabic{enumii}.]
   \item Gormley M., \textbf{Dampier W.}, Ertel A., Karacali B., Tozeren A. Prediction potential of candidate biomarker sets identified and validated on gene expression data from multiple datasets. BMC Bioinformatics, Oct. 2007; 8:415 Cited by 17
   \item \textbf{Dampier W.}, Tozeren A. Signaling perturbations induced by invading H. pylori proteins in the host epithelial cells: A mathematical modeling approach. Journal of Theoretical Biology, Sept. 2007; 248(1):130 Cited by 8
   \item Layton B., D'Souza A., \textbf{Dampier W.}, Zeiger A., Sabur A., Jean-Charles J. Collagen's triglycine repeat number and phylogeny suggest an interdomain transfer event from a Devonian or Silurian organism into Trichodesmium erythraeum. J Mol Evol. June 2008; 66(6):539. Cited by 7
   \item Evans P., \textbf{Dampier W.}, Ungar L., Tozeren A. Prediction of HIV-1 virus-host protein interactions using virus and host motifs. BMC Med Genomics, May 2009; 2:27 Cited by 34, Highly Accessed (As determined by Biomed Central)
   \item \textbf{Dampier W.}, Evans P., Ungar L., Tozeren A. Host sequence motifs shared by HIV-1 predict patient response to antiretroviral therapy. BMC Med Genomics, July 2009; 2:47 Cited by 13
   \item Zhou J., Wang C., Wang Z., \textbf{Dampier W.}, Wu K., Casimiro M., Chepelev L., Popov V., Quong A., Tozeren A., Zhao K., Lisanti M., Pestell R. Attenuation of Forkhead Signaling by the Retinal Determination Factor DACH1. Proceedings of the National Academy of Sciences, March 2010 Cited by 13
   \item Dawany N., \textbf{Dampier W.}, Tozeren A. Large-scale integration of microarray data reveals genes and pathways common to multiple cancer types. Int J Cancer. Dec 2010. Cited by 12
   \item Sarmady M., \textbf{Dampier W.}, Tozeren A. HIV Protein Sequence Hotspots for Crosstalk with Host Hub Proteins PLOS One. June 2011, Cited by 5
   \item Sarmady M., \textbf{Dampier W.}, Tozeren A. Sequence- and Interactome- Based Prediction of Viral Protein Hotspots Targeting Host Proteins: A Case Study for HIV Nef. PLOS One. June 2011, Cited by 2
   \item Casimiro MC., Crosariol M., Loro E., Ertel A., Yu Z., \textbf{Dampier W.}, Saria EA., Pestell R. ChIP sequencing of cyclin D1 reveals a transcriptional role in chromosomal instability in mice, The Journal of Clinical Investigation 122 (3), 833, March 2011, Cited by 16
   \item Smith SB., \textbf{Dampier W.}, Tozeren A., Brown JR., Magid-Slav M. Identification of Common Biological Pathways and Drug Targets Across Multiple Respiratory Viruses Based on Human Host Gene Expression Analysis. PloS one 7 (3), e33174. March 2011, Cited by 14
   \item Clark PM., Dawany N., \textbf{Dampier W.}, Byers SW., Pestell RG., Tozeren A. Bioinformatics analysis reveals transcriptome and microRNA signatures and drug repositioning targets for IBD and other autoimmune diseases. Inflammatory Bowel Diseases, June 2012, Cited by 5
  \end{enumerate}
  \item[] Abstracts
  \begin{enumerate}[label=\arabic{enumii}.]
   \item Aiamkitsumrit B., Nonnemacher M., Pirrone V., Zhong W., Frantz B., Rimbey M., Passic S., Blakey B., Parikh N., Martin-Garcia J., Downie D., Lewis S., Jacobson J., Moldover B., \textbf{Dampier W.}, Wigdahl B. Identification of HIV-1 X4, R5, and R5 subgroup genetic signatures in the viral promoter, Tat, and Vpr. University of Pennsylvania CFAR 11th Annual Research Retreat, Philadelphia, PA, December 3, 2012
   \item \textbf{Dampier W.}, Nonnemacher M.,, Pirrone V., Williams J., Aiamkitsumrit B., Wojno A., Passic S., Blakey B., Zhong W., Moldover B., Feng R., Downie D., Lewis S., Jacobson J., Wigdahl B.  Impact of substance abuse on HIV-1 LTR single nucleotide polymorphisms (SNPs) and disease progression in a clinical cohort.  Society for Neuroimmune Pharmacology 18th Scientific Conference, San Juan, Puerto Rico, April 3-6, 2013.
   \item Nonnemacher M., Pirrone V., \textbf{Dampier W.}, Aiamkitsumrit B., Williams J., Shah S., Wojno A., Passic S., Blakey B., Zhong W., Moldover B., Feng R., Downie D., Lewis S., Jacobson J., Wigdahl B.  HIV-1 LTR single nucleotide polymorphisms (SNPs) correlate with clinical disease parameters. Society for Neuroimmune Pharmacology 18th Scientific Conference, San Juan, Puerto Rico, April 3-6, 2013.
   \item Antell G., Nonnemacher M., Pirrone V., \textbf{Dampier W.}, Aiamkitsumrit B., Williams J., Shah S., Wojno A., Passic S., Blakey B., Zhong W., Moldover B., Feng R., Downie D., Lewis S., Jacobson J., Wigdahl B.  HIV-1 LTR single nucleotide polymorphisms (SNPs) that correlate with clinical disease parameters are found in both the peripheral blood and brain compartments.  Society for Neuroimmune Pharmacology 18th Scientific Conference, San Juan, Puerto Rico, April 3-6, 2013.
   \item Nonnemacher M., Strazza M., Pirrone V., Lin W., Feng R., \textbf{Dampier W.}, Wigdahl B.  Use of an in vitro model of the blood brain barrier to examine the effects of aging.  Translational Medicine \& Applied Biotechnology Workshop on Cognition and Aging, Drexel University College of Medicine, Philadelphia, PA, June 5, 2013.
   \item Pirrone V., Nonnemacher M., Passic S. R., Parikh N., Aiamkitsumrit B., \textbf{Dampier W.}, Katsikis P., Mueller Y., Sell C., Libon D., Moldover B., Feng R., Jacobson J. M., Wigdahl B.  Aging in the HIV-1-infected population: Impact on markers of HIV-1 disease.  Translational Medicine \& Applied Biotechnology Workshop on Cognition and Aging, Drexel University College of Medicine, Philadelphia, PA, June 5, 2013.
   \item Aiamkitsumrit B., Nonnemacher M., Pirrone V., Zhong W., Frantz B., Rimbey M., Passic S., Blakey B., Parikh N., Martin-Garcia J., Downie D., Lewis S., Jacobson J. M., Moldover B., \textbf{Dampier W.}, Wigdahl B. Identification of HIV-1 X4, R5, and R5 subgroup genetic signatures in the LTR, Tat, and Vpr.  2013 International Symposium on Molecular Medicine and Infectious Disease, Drexel University College of Medicine, Philadelphia, PA, June 17-21, 2013.
   \item Antell G., Nonnemacher M., Pirrone V., \textbf{Dampier W.}, Aiamkitsumrit B., Williams J., Shah S., Wojno A., Passic S., Blakey B., Zhong W., Moldover B., Feng R., Downie D., Lewis S., Jacobson J., Wigdahl B. HIV-1 LTR single nucleotide polymorphisms (SNPs) that correlate with clinical disease parameters are found in both the peripheral blood and brain.  2013 International Symposium on Molecular Medicine and Infectious Disease, Drexel University College of Medicine, Philadelphia, PA, June 17-21, 2013.
   \item Parikh N., \textbf{Dampier W.}, Feng R., Passic S., Zhong W., Frantz B., Aiamkitsumrit B., Pirrone V., Nonnemacher M., Jacobson J. M., Wigdahl B. Cocaine alters cytokine profiles within HIV-1-infected African American individuals in the DREXELMED HIV/AIDS Genetic Analysis Cohort 2013 International Symposium on Molecular Medicine and Infectious Disease, Drexel University College of Medicine, Philadelphia, PA, June 17-21, 2013.
   \item Williams J., \textbf{Dampier W.}, Nonnemacher M., Pirrone V., Aiamkitsumrit B., Wojno A., Passic S., Blakey B., Zhong W., Moldover B., Feng R., Downie D., Lewis S., Jacobson J. M., Wigdahl B. Impact of substance abuse on HIV-1 LTR single nucleotide polymorphisms (SNPs) and disease progression in a clinical cohort.  2013 International Symposium on Molecular Medicine and Infectious Disease, Drexel University College of Medicine, Philadelphia, PA, June 17-21, 2013.
   \item Aiamkitsumrit B., Nonnemacher M., Zhong W., Russo T., Pirrone V., Frantz B., Rimbey M., Passic S., Blakey B., Parikh N., Martin-Garcia J., Jacobson J., Moldover B., \textbf{Dampier W.}, Wigdahl B. Differential HIV-1 X4 and R5 genetic signatures within the LTR, Tat and Vpr. Journal of Neurovirology, Washington DC, October 25-30, 2013.
   \item \textbf{Dampier W.}, Parikh N., Nonnemache, M., Pirrone V., Williams J., Aiamkitsumrit B., Passic S., Zhong W., Moldover B., Feng R., Jacobson J., Wigdahl B. Longitudinal analysis of the impact of substance abuse on HIV-1-associated neurological decline in the DrexelMed HIV/AIDS Genetic Analysis Cohort. Journal of Neurovirology, Washington DC, October 25-30, 2013.
   \item Parikh N., \textbf{Dampier W.}, Feng R., Passic S., Zhong W., Aiamkitsumrit B., Pirrone V., Nonnemacher M., Jacobson J., Wigdahl B. Cocaine alters immunomodulatory profiles within HIV-1-infected African American individuals in the DREXELMED HIV/AIDS Genetic Analysis Cohort. Journal of Neurovirology, Washington DC, October 25-30, 2013.
   \item Zhong W., Pirrone V., Nonnemacher M., Parikh N., Aiamkitsumrit B., \textbf{Dampier W.}, Katsikis P., Mueller Y., Sell C., Libon D., Moldover B., Feng R., Jacobson J., Wigdahl B. Impact of Aging on markers of HIV-1 disease. Journal of Neurovirology, Washington DC, October 25-30, 2013.
   \item Williams J., \textbf{Dampier W.}, Nonnemacher M., Pirrone V., Aiamkitsumrit B., Wojno A., Passic S., Blakey B., Zhong W., Moldover B., Feng R., Downie D., Lewis S., Jacobson J., Wigdahl B. Use of drugs of abuse impact HIV-1 LTR single nucleotide polymorphisms (SNPs) in the DrexelMed HIV/AIDS Genetic Analysis Cohort. Journal of Neurovirology, Washington DC, October 25-30, 2013.
   \item Antell G., Nonnemacher M., Pirrone V., \textbf{Dampier W.}, Aiamkitsumrit B., Williams J., Shah S., Passic S., Blakey B., Zhong W., Moldover B., Feng R., Jacobson J., Wigdahl B. Multiple HIV-1 LTR single nucleotide polymorphisms (SNPs) that occur in peripheral blood and correlate with disease severity are also present in infected brain samples. Journal of Neurovirology, Washington DC, October 25-30, 2013.
   \item Pirrone V., Nonnemacher M., \textbf{Dampier W.}, Aiamkitsumrit B., Williams J., Shah S., Passic S., Blakey B., Zhong W., Moldover B., Feng R., Jacobson J., Wigdahl B. HIV-1 LTR single nucleotide polymorphisms (SNPs) correlate with clinical disease parameters. Journal of Neurovirology, Washington DC, October 25-30, 2013.
  \end{enumerate}

 \end{itemize}

 \item RESEARCH PRESENTATIONS
 \begin{itemize}
  \item[] Oral Presentations by Invitation \newline
  \noindent
   \begin{tabular}{p{0.15\textwidth}p{0.01\textwidth}p{0.65\textwidth}}
  2009 & & A Machine Learning Technique for the Classification of Therapeutic Interventions for HIV-1 Patients. \newline Villanova Computer Science Colloquium \newline Villanova, Pennsylvania \\
  \\
  2009 & & Classification of Therapeutic Response in HIV-1 Patients Using Functional Motifs. \newline GPBA Annual Research Retreat \newline Philadelphia, Pennsylvania \\
  \\
  2010 & & Co-Evolution in Viral Genomes. \newline GlaxoSmithKline Invited Lecture. \newline 	Philadelphia, Pennsylvania \\
  \\
  2011 & & Computational Analysis Pipelines in Python. \newline Invited Tutorial Children’s Hospital of Philadelphia \newline Philadelphia, Pennsylvania \\
  \end{tabular}
  \item[] Invited Lectures \newline
   \begin{tabular}{p{0.15\textwidth}p{0.01\textwidth}p{0.65\textwidth}}
   2008 & & Multiple Alignments from a Bioinformatics Perspective. \newline Department of Electrical Engineering at Drexel University. \newline Invited lecture for Genomics Signals Processing ECE-690 \newline 	Philadelphia, Pennsylvania \\
   \\
   2008 & & An Overview of Molecular Evolution. \newline Department of Mechanical Engineering at Drexel University. \newline Invited lecture for MechanoEvolution MEM-380 \newline Philadelphia, Pennsylvania \\
   \\
   2010 & & Quantitative Methods for Analyzing Biological Reactions. \newline Invited Lecture, Izmir Institute of Technology \newline Izmir, Turkey \\
  \end{tabular}
 \end{itemize} 
\end{enumerate}
\end{document}
